### 2025-08-09 getting-started.qmd
20250809 - Rglpk

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","grid","patchwork",
     "pROC", "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats",
     "AICcmodavg","rstan","brms","tidybayes","bbmle","fitdistrplus","sn",
     "mclust","magrittr","viridis","viridisLite","msir","plotly","webshot2",
     "quantmod","fPortfolio","NMOF","nFactors","xts","zoo","forecast","stringi",
     "parallelly","doParallel","missRanger","ggridges","powerjoin","caret",
     "LongituRF","gpboost","mgcv","rms","car","lavaan","lavaanPlot","lavaangui",
     "mice","miceadds","interactions","robustbase","ordinal","MASS",
     "data.table","future","future.apply","SimDesign","domir","GGally"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

>>>>

   install.packages(c(
     "petersenlab","remotes","knitr","rmarkdown","tidyverse","nflverse",
     "tidymodels","easystats","broom","broom.mixed","psych","downlit","xml2",
     "gsisdecoder","progressr","DescTools","pwr","pwrss","WebPower","XICOR",
     "dagitty","ggdag","ggtext","gghighlight","ggExtra","grid","patchwork",
     "pROC", "lme4","lmerTest","MuMIn","emmeans","pbkrtest","sjstats",
     "AICcmodavg","rstan","brms","tidybayes","bbmle","fitdistrplus","sn",
     "mclust","magrittr","viridis","viridisLite","msir","plotly","webshot2",
     "quantmod","fPortfolio","NMOF","nFactors","xts","zoo","forecast","stringi",
     "parallelly","doParallel","missRanger","ggridges","powerjoin","caret",
     "LongituRF","gpboost","mgcv","rms","car","lavaan","lavaanPlot","lavaangui",
     "mice","miceadds","interactions","robustbase","ordinal","MASS",
     "data.table","future","future.apply","SimDesign","domir","GGally","Rglpk"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false
